Review of Group 8 by Group 1

### 2015-02-10 rmtw/a3/latex8.tex
Added notes for meth section

Steps\&Phases
1. Case study design: Objectives are defined and the case study is planned.

>>>>

Steps \& Phases
1. Case study design: Objectives are defined and the case study is planned. 
Runesson+Höst mention the importance of carefully planning case studies, despite them being of the flexible type. 
Planning consists of which methods to use for the data collection, which departments to visit, which documents to read, who to interview, when interviews should be conducted, etc. These can be formulated in a case study protocol. 
It should contain: 
Objective: What to achieve?
The case: What is studied?
Theory: Frame of reference?
Research questions: What to know?
Methods: How to collect data?
Selection strategy: Where to seek data?

2. Preparation for data collection: procedures and protocols for data collection are defined
3. Collecting evidence: Execution with data collection on the studied case
A direct method (first degree) (Lethbridge et al. 2005) will be used. (Interviews).
Third degree (Lethbridge et al. 2005) can also be used. I.e. analyse work artifacts. (The time-to-market based on requirments thing). (More info page 19)

Mix of open/closed questions + semi-structured.

4. Analysis of collected data
Analysis will be done in tandem with the data gatheritng to be able to iteratively improve the data collection process+tools

Hypothesis generation will be an important part of the data analysis, since the outcome/goal of the study is not clear.

5. Reporting
(Descriptions on page 8 of the pdf in runessson host paper)

Case study protocol
\#	Goals and Scope		Data collection and filtering	Analysis and presentation	Interpretation and Improvement
(More info on Page 11 of the host pdf)

Mention stuff about ethical problems (page 12)
